Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-16 paper.tex
figures correctly placed

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. Security
of containers is still most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Except web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping focus on HPC environments. This popularity of containers lead us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters}.

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
\begin{comment}
Malware is a computer software that is specially designed to attack the target computer,
whereas 
\end{comment}
Vulnerability is a weakness in the developer's software that can be used
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field, and access their
related risks for data analysis. Particularly, we aim to answer three primary
research questions:

@@

@@

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.

@@

\subsection{Effect Of Update}
\begin{comment}
The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
\end{comment}

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
\begin{figure*}
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
	after update of the images}
      \end{figure*}
\subsection{Effect Of Size Reduction}

Our last experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.

\begin{figure*}
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number, however they cannot
be made invulnerable.

>>>>

However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
are used by containers to mitigate these threats to a certain extent. Security
of containers is still most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
done in January 2015, security is the
biggest concern while deploying containers.
Except web applications, containers are also popularly used for scientific computing
and data science in neuroscience. In fact, Singularity was developed for scientific applications
by keeping focus on HPC environments. This popularity of containers lead us to the
primary research question of this work: \textit{what is the current security state of
container images that are deployed on HPC clusters?}.

To answer that question, we scan images that are used on Compute
Canada clusters by neuroscience field. Scanning refers to the practice of
collecting all information about the container image, investigating it
for vulnerabilities, and finally producing a
report to summarize scanning results. It is broadly categorized into
two types: static scanning and dynamic scanning. The former scanning technique
involves extracting information of an image without running it into a container,
whereas the latter approach involves launching the container from the target image, and
then scanning the running container.
Here, we focus mainly on vulnerability scanning.
Vulnerability is a weakness in the developer's software that can be used
by the attacker to perform unathorized actions on the target computer.
In this paper, we report all vulnerabilities that are present in
container images, specifically used by neuroimaging field. Particularly,
we aim to answer four primary research questions:

@@

\textit{RQ4:} Can we get rid of these vulnerabilities by both updating
and shrinking image size?

@@

\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
\begin{figure*}[b]
        {\includegraphics[width=\textwidth]
        {Figures/vulnwithupdate.pdf}}
        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
        after update of the images}
      \end{figure*}

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}
\subsection{Effect Of Update}
\begin{comment}
The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
\end{comment}

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
%\begin{figure*}[h]
%        {\includegraphics[width=\textwidth]
%        {Figures/vulnwithupdate.pdf}}
%        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
%	after update of the images}
%      \end{figure*}

\subsection{Effect Of Size Reduction}

Our third experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.

\subsection{Effect Of Update and Size Reduction}

Our last experiment includes updating the image and then removing unnecessary packages from it.
Our initial thought was that it will reduce the number of vulnerabilities significantly. Howver
we analyzed that this is not always true. It depends on which packages you are deleting and how
many vulnerabilities they contain. In particular, if a package contains a large number of vulnerabilities
it means deleting that package will help to reduce vulnerabilities in that image by a significant number.
Contrary

@@

In this paper, we performed various experiments to study the security state of the Docker
and Singularity images, which are used in the neuroimaging field. We found out strong correlation
between the number of packages and the number of vulnerabilities in the images, which implies
that the number of vulnerabilities increases with the number of packages. We also found out that
updating images reduces the number of vulnerabilities by a significant number. However, for some
vulnerabilities there are no fixes available yet so the images cannot 
be made totally invulnerable. Continuing with our next experiment of minification, we thought that
it will decrease vulnerabilities by a significant number. However, we found out that this is not
the case always.
